---
title: "quick_and_dirty_monitor"
output: html_document
---

## 0) Data Preperation 

```{r}
#Call any libraries
library(ggplot2)
library(nlme)

#Clean up the dataset

#First, get rid of the technical glitches in which no-one was paired up w/ a parnter.
moverData <- read.csv("v2_mover_date_master.csv")
masterData <- read.csv("v2_monitor_data_master.csv")
tech_excl_before <- nrow(masterData)
masterData <- masterData[masterData$computer_overall_speed != -1,]
tech_excl_after <- nrow(masterData)


tech_excl_after - tech_excl_before
```

Good - only 7 people were excluded because they weren't assigned a valid partner.

```{r}
#Now, let's make some variables

# a) Monitor Z-Scores
masterData$monitor_completion_time_z <- (masterData$completion_time - mean(masterData$completion_time))/sd(masterData$completion_time)

# b) Mover z-scores. Base it on values FROM moverData and NOT from masterData, as masterData
# has nested data
masterData$mover_completion_time_z <- (masterData$computer_solo_time/100 - mean(moverData$completion_time))/sd(moverData$completion_time)



# Improvement Index - Monitor
masterData$improvement_index <- 
  masterData$second_half_avg_speed - masterData$first_half_avg_speed

# Improvement Index - Mover (both datasets)
masterData$computer_improvement_index <- 
  masterData$computer_avg_speed_second_half - masterData$computer_avg_speed_first_half
moverData$improvement_index <- 
  moverData$second_halv_avg_speed - moverData$first_half_avg_speed
masterData$computer_improvement_index_z <- (masterData$computer_improvement_index - mean(moverData$improvement_index))/sd(moverData$improvement_index)


# Improvement after switch index - Mover (both datasets)
masterData$computer_post_switch_improvement_index <- 
  masterData$computer_avg_speed_after_switch - masterData$computer_avg_speed_before_switch

```

```{r}
#Next, let's grab a few of the mover's survey responses...

#First, initialize the new column
masterData$computer_switch_goodbad <- NA

#Next, go through all the movers and get the ID and VARIABLE o fitnerest
for(counter in c(1:nrow(moverData))){
  id_of_interest <- moverData$participant_id[counter]
  value <- moverData$switch_goodbad[counter]
  
  #Now that we have those vlaues, go through each row of our monitor data...  
  for (counter in c(1:nrow(masterData))){
    current_id <- masterData$computer_id[counter]
    
    #If a match is found, replace that row with the proper value from the previous loop
    if(current_id == id_of_interest){
      masterData$computer_switch_goodbad[counter] <- value
    }
  }#end of for(masterData)
}#end of for(moverData)

#Finally, let's recode the variable.
masterData[masterData$computer_switch_goodbad == 1,]$computer_switch_goodbad <- "Partner didn't want switch"
masterData[masterData$computer_switch_goodbad == 2,]$computer_switch_goodbad <- "Partner wanted switch"
```

```{r}
#Finally, let's exclude other faulty data

#First, exclude those who switched tabs, at it gives away the human-partner illusion
masterDataExclusions <- subset(masterData, !switched_tabs_critical)
#Next, exclude those who thought they were paired with a bot.
masterDataExclusions <- subset(masterDataExclusions, !bot_partner)

#Let's also divide the real data (masterDataExclusions) into movers vs. non-movers
masterDataExclusions_non_switchers <- 
  subset(masterDataExclusions, masterDataExclusions$game_mode == 2)
masterDataExclusions_switchers <- 
  subset(masterDataExclusions, masterDataExclusions$game_mode == 3)

nrow(masterData) - nrow(masterDataExclusions)
```

Wow. 72 exclusions, meaning my sample size should now be around 140.

## 1) How did people perform on the maze? 

### First, let's look at the movers vs. monitors
```{r}
par(mfrow = c(2,2))
#Movers
boxplot(moverData$completion_time, main = "Dist of Mover Completion Time",
        ylab = "Completion Time (s)")
hist(moverData$completion_time, main = "Freq of Mover Completion Time",
     xlim=c(0,200), xlab = "Completion Time (s)")
abline(v=mean(moverData$completion_time), col="Red")

#Monitors
boxplot(masterDataExclusions$completion_time, main = "Dist of monitor Completion Time",
        ylab = "Completion Time (s)")
hist(masterDataExclusions$completion_time, main = "Freq of monitor completion Time",
     xlim=c(0,200), xlab = "Completion Time (s)")
abline(v=mean(masterDataExclusions$completion_time), col = "Red")

par(mfrow = c(1,1))
```

How intruiging! Both graphs looks extremely similar, both in terms of mean and in terms of distributions.

```{r}
mover_mean <- mean(moverData$completion_time)
monitor_mean <- mean(masterDataExclusions$completion_time)

paste("Mover Mean =", mover_mean, "Monitor Mean =", monitor_mean, sep = " ")
```

The means are extreme similar; it seems that switching doesn't really effect performance. There's more going on than meets the eye though. How does the performance of switchers compare to that of non switchers

### How does the performance of switchers compare to non-switchers?

```{r}
par(mfrow=c(2,2))
barplot(prop.table(table(masterDataExclusions$switch)), ylab = "Proportion", main = "Did the switch happen?")
boxplot(masterDataExclusions$completion_time ~ masterDataExclusions$switch, main = "Switch vs. no-switch distributions", ylab = "Completion time (s)")
hist(masterDataExclusions_non_switchers$completion_time, 
     main = "Freq of monitor completion Time", xlim=c(0,200), xlab = "Completion Time (s)")
abline(v=mean(masterDataExclusions_non_switchers$completion_time), col = "Red")
hist(masterDataExclusions_switchers$completion_time, 
     main = "Freq of monitor completion Time", xlim=c(0,200), xlab = "Completion Time (s)")
abline(v=mean(masterDataExclusions_switchers$completion_time), col = "Red")

par(mfrow=c(1,1))
```

```{r}
switch_mean <- mean(masterDataExclusions_switchers$completion_time)
no_switchmean <- mean(masterDataExclusions_non_switchers$completion_time)

paste("Switch Mean =", switch_mean, "No Switch Mean =", no_switchmean, 
      "SD of masterData =", sd(masterDataExclusions$completion_time), sep = " ")
```

Holy crap! Switching makes yo udo WORSE by 30 seconds!! That's bascially a whole fricken standard deviation!!!


```{r}
#Let's correct for these nasty nested data effects
mlreg = lme(completion_time ~ switch, data = masterDataExclusions, random=~1|computer_id)
summary(mlreg)
```

INCREDIBLE!!!!!! Even when controlling for the nested nature of the data, SWITCHERS DO WORSE THAN NON-SWITCHERS BY A WHOLE 21 SECONDS!!!!!!!!!!!!!!!!!!!!

## 2) Why cuases someone to press the "switch" button?

### Surely it's completion time, or an objectiv emeasure of performance?

```{r}
par(mfrow=c(1,2))

#Completion Time (s)
plot(game_mode ~ I(computer_solo_time/100), data = masterDataExclusions, main = "Switching vs. Mover CT", xlab = "Mover Completion Time (s)")
abline(lm(game_mode ~ I(computer_solo_time/100), data = masterDataExclusions), col = "red")

#Completion Time Zs
plot(game_mode ~ mover_completion_time_z, data = masterDataExclusions, main = "Switching vs. Mover CT", xlab = "Mover Completion Time (z)")
abline(lm(game_mode ~ mover_completion_time_z, data = masterDataExclusions), col = "red")

par(mfrow=c(1,1))
```


```{r}
#Show me the mixed linear effects for Z SCORES!
mlreg = lme(game_mode ~ mover_completion_time_z, data = masterDataExclusions, random=~1|computer_id)
summary(mlreg)
```

No way!!! For every one standard deviation increase in performance (i.e. the user does worse on the maze by 1 sd, meaning the ytake longer to complete it), the user becomes roughly 9% more likely to switch. HOWEVER, THIS EFFECT IS INSIGINIFICANT, even with a sample size of 150 participants!

Short answer: the mover's performance has NOTHING to do with completion time!

### Ok, why don't we look at all the variables together?
```{r}
mlreg <- lme(game_mode ~ I(computer_solo_time/100) + computer_total_reset_counter + computer_total_pixel_movement +  computer_overall_speed + computer_improvement_index, data = masterDataExclusions, random=~1|computer_id)

summary(mlreg)
```

```{r}
mean(masterDataExclusions$computer_total_reset_counter)
```

How disappointing: NONE of these values explain why people chose to switch versus not swtich. The only thing that sort of explains it is the computer's total reset counter, but even then, running into a wall only makes one 3% more likely to switch roles PER HIT. The average person htis a wall 3-4 times, so it's not like it has a strong effect.

## 3) WITHIN the switch condition, what are the effects of switching?

### Let's use improvement indexes. First, we need to establish what it means.
```{r}
#First of all, let's convert these 'improvement indexes' into meaningful units
masterDataExclusions_switchers$improvement_index <- 
  masterDataExclusions_switchers$improvement_index * 1000
masterDataExclusions_switchers$computer_improvement_index <- 
  masterDataExclusions_switchers$computer_improvement_index * 1000
masterDataExclusions_switchers$computer_post_switch_improvement_index<- 
  masterDataExclusions_switchers$computer_post_switch_improvement_index * 1000

#Next, let's see how this relates to completion_time
```

```{r}
par(mfrow=c(1,3))
#Monitors
eq <- completion_time ~ improvement_index
plot(eq , data = masterDataExclusions_switchers, ylab = "Completion Time (s)", xlab = "Improvement Index", main = "Monitors")
mon_impr_ind_reg <- lm(eq, data = masterDataExclusions_switchers)
abline(mon_impr_ind_reg, col = "red")

#Movers (Improvement)
eq <- I(computer_solo_time/100) ~ computer_improvement_index
plot(eq , data = masterDataExclusions_switchers, ylab = "Completion Time (s)", xlab = "Improvement Index", main = "Movers - Improvement Index")
mov_impr_ind_reg <- lm(eq, data = masterDataExclusions_switchers)
abline(mov_impr_ind_reg, col = "red")

#Movers (post-switch)
eq <- I(computer_solo_time/100) ~ computer_post_switch_improvement_index
plot(eq , data = masterDataExclusions_switchers, ylab = "Completion Time (s)", xlab = "Post Switch Improvement Index", main = "Movers - Post Switch Improvement Index")
mov_post_switch_impr_ind_reg <- lm(eq, data = masterDataExclusions_switchers)
abline(mov_post_switch_impr_ind_reg, col = "red")
par(mfrow=c(1,1))
```

Ok - so it looks like that the more you improve, the better your time gets. Let's seeexactly how much

```{r}
#For computer
summary(lme(I(computer_solo_time/100) ~ computer_improvement_index, data = masterDataExclusions_switchers, random=~1|computer_id))
```
#2) Why do people switch?


```{r}
#Let's correct for these nasty nested data effects
mlreg = lme(completion_time ~ switch, data = masterDataExclusions, random=~1|computer_id)
summary(mlreg)
```




```{r}

ggplot(masterDataExclusions, aes(x = computer_name, y = switch, color = effects_of_switch > 0)) + geom_point(position = position_jitter(w = 0, h = .1)) + facet_wrap(~computer_switch_goodbad, scales="free") + scale_color_manual(values=c("green","red")) + labs(colour = "Switching Hurt Performance?") + xlab("Partner Name") + ylab("Did the switch happen?")




```





DEklokijklkljljkljkljkljjkljklklj